Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-07 paper_jasa.tex
subject specific power curves added

@@

\begin{figure}[hbtp]
   \centering
       \scalebox{0.40}{\includegraphics{power_model.pdf}}
       \caption{Estimated power curve from Equation \ref{eqn:power} along with 95\% confidence interval for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
       \label{fig:power_model}
\end{figure}

%We fit model \eqref{mixed} to the survey data obtained from the simulation experiment. The estimated overall power curve obtained from equation \eqref{eqn:power} is shown in Figure \ref{fig:power_model}. Model \ref{mixed} also gives the subject specific power curves shown in Figure \ref{fig:power_subject}. The plot includes 20 randomly selected subject-specific power curves. Notice that the power curve estimated for one subject is above the UMP test power curve.

\begin{figure}[hbtp]
   \centering
       \scalebox{0.45}{\includegraphics{power_subject.pdf}}
       \caption{Estimated subject specific power curve from model \ref{mixed} for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
       \label{fig:power_subject}
\end{figure}

>>>>

\begin{figure}[hbtp]
   \centering
       \scalebox{0.60}{\includegraphics{power_screening_subject.pdf}}
       \caption{The subject wise power estimated from model \ref{mixed} are shown for various data sets obtained by applying 5 screening criteria.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown in pink lines for comparison.}
       \label{fig:power_screening_subject}
\end{figure}

%\begin{figure}[hbtp]
%   \centering
%       \scalebox{0.40}{\includegraphics{power_model.pdf}}
%       \caption{Estimated power curve from Equation \ref{eqn:power} along with 95\% confidence interval for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
%       \label{fig:power_model}
%\end{figure}

%We fit model \eqref{mixed} to the survey data obtained from the simulation experiment. The estimated overall power curve obtained from equation \eqref{eqn:power} is shown in Figure \ref{fig:power_model}. Model \ref{mixed} also gives the subject specific power curves shown in Figure \ref{fig:power_subject}. The plot includes 20 randomly selected subject-specific power curves. Notice that the power curve estimated for one subject is above the UMP test power curve. 
%
%\begin{figure}[hbtp]
%   \centering
%       \scalebox{0.45}{\includegraphics{power_subject.pdf}}
%       \caption{Estimated subject specific power curve from model \ref{mixed} for sample size $n$ = 100 and $\sigma$ = 12.  The corresponding power curve for Uniformly Most powerful (UMP) test is shown for comparison.}
%       \label{fig:power_subject}
%\end{figure}

@@
